Writing a reproducible paper with Quarto

### 2023-02-17 paper.qmd
Update author and date.

---
title: "Writing a reproducible paper with Quarto"
author: "Paul C. Bauer, Camille Landesvatter"
format: html
date: 'First version: 16 February, 2023<br>This version: `r format(Sys.time(), "%d %B, %Y")`'
abstract: 'The present paper provides a template to write a reproducible scientific paper with Quarto. It is based on earlier Pagedown/RMarkdown templates that can be downloaded [here](https://osf.io/k8jhx/) [@Bauer2018-dl] and [here](https://osf.io/q395s) [@Bauer2021-dl]. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s?usp=sharing). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/).'
bibliography: references.bib
tbl-cap-location: top
execute: 
  echo: false
  warning: false
  message: false
---

>>>>

---
title: "Writing a reproducible paper with Quarto"
author:
  - name: Paul C. Bauer
    orcid: 0000-0002-8382-9724
    email: mail@paulcbauer.de
    affiliations:
      - name: Mannheim Centre for European Social Research
  - name: Camille Landesvatter
    orcid: 0000-0003-0156-5364
    email: camille.landesvatter@uni-mannheim.de
    affiliations:
      - name: Mannheim Centre for European Social Research
format: html
date: 'last-modified'
date-format: "[First version:February  16, 2023<br>This version:] MMMM D, YYYY"
abstract: 'The present paper provides a template to write a reproducible scientific paper with Quarto. It is based on earlier Pagedown/RMarkdown templates that can be downloaded [here](https://osf.io/k8jhx/) [@Bauer2018-dl] and [here](https://osf.io/q395s) [@Bauer2021-dl]. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s?usp=sharing). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/).'
bibliography: references.bib
tbl-cap-location: top
execute: 
  echo: false
  warning: false
  message: false
---
